Refractory anaphylaxis: Data from the European Anaphylaxis Registry

### 2019-08-29 analysis/paper/paper.Rmd
figures and acknowledgements

`r elicitorTab[elicitorTab$Elicitor =="food","Food allergy [n]"] / elicitorTab[elicitorTab$Elicitor =="food","n"]*100 %>% {round(.,1)}`% of food elicited refractory cases had a previously confirmed diagnosis of food allergy. Insect-venom and food allergens most frequently elicited severe cases of anaphylaxis.
Refractory anaphylaxis cases were more often elicited by bees than severe, non-refractory cases, p = `r table(data3$q_340_insects,data3$rANA) %>%  {rbind(addmargins(.[3:8,],1) %>% tail(1),.[2,])} %>% as.matrix() %>% fisher.test() %>% {.$p.value} %>% round(4)` (table \@ref(tab:elicitExact)).

@@

<!-- The influence of tryptase -->
Baseline serum tryptase (BST) levels were increased in patients with refractory anaphylaxis, although only in 7 patients they were over the threshold level of 11.5 ng/mL - what is commonly recognized as elevated [@klion2003]. BST may reflect pro-β tryptase due to increased body mast cell content [@CAUGHEY2006] or result from alpha-tryptasemia due to multiple copies of *TPSAB1* gene [@Lyons2018]. Irrespective of the mechanism - increased BST has been shown to correlate with the severity of anaphylaxis [@Aniceto2019].

@@

# Acknowledgements
We thank all patients, parents, and their children for their support in providing data on the
the occurrence of anaphylaxis for this study. We thank the study personnel for patients
counseling and data entry and we thank the members of The European Anaphylaxis Registry
in detail:
J. Grünhagen (Berlin, Germany),
K. Beyer (Berlin, Germany),
A. Möser (Jena, Germany),
T. Fuchs (Göttingen, Germany),
F. Ruëff (Munich, Germany),
B. Wedi (Hanover, Germany),
F. Friedrichs (Aachen, Germany),
H. Dickel (Bochum, Germany),
H. Merk (Aachen, Germany),
U. Hillen (Essen, Germany),
A. Bauer (Dresden, Germany),
N. Wagner (Erlangen, Germany),
E. Rietschel (Cologne, Germany),
R. Treudler, S. Aurich (Leipzig, Germany),
L. Klimek, O. Pfaar (Wiesbaden, Germany),
N. Reider (Innsbruck, Germany),
W. Aberer (Graz, Austria),
A. Köhli (Zurich, Switzerland),
F. Riffelmann (Schmallenberg, Germany),
B. Kreft (Halle, Germany),
K. Nemat (Dresden, Germany),
T. Kinaciyan (Vienna, Austria),
R. Brehler (Münster, Germany),
J. Witte (Hamburg, Germany),
N. Hunzelmann und I. Huseynow (Cologne, Germany),
T. Bieber (Bonn, Germany),
U. Rabe (Treuenbritzen, Germany),
P. Schmid-Grendelmeier (Zurich, Switzerland),
W. Brosi (Würzburg, Germany),
S. Nestoris (Lippe-Lemgo, Germany),
T. Hawranek (Salzburg, Austria),
R. Bruns (Greifswald, Germany),
S. Lehmann (Aachen, Germany),
L. Lange (Bonn, Germany),
G. Hansen (Hanover, Germany),
C. Pföhler (Homburg, Germany),
E. Varga (Graz, Austria),
Z. Szepfalusi (Vienna, Austria),
P. Eng (Aarau, Switzerland),
P. Eng (Lucerne, Switzerland),
T. Reese (Rheine, Germany),
M. Polz (Rüsselsheim, Germany),
S. Schweitzer-Krantz (Düsseldorf, Germany),
H. Rebmann (Tübingen, Germany),
G. Stichtenoth (Lübeck, Germany),
S. Theis (Schwedt, Germany),
I. Yildiz (Neumünster, Germany),
M. Gerstlauer (Augsburg, Germany),
A. Nordwig (Dresden, Germany),
R. Schlags (Wangen im Allgäu, Germany),
I. Neustädter (Fürth, Germany),
C. Stadlin (Zurich, Switzerland),
M. Bücheler (Bonn, Germany),
S. Volkmuth (Velbert, Germany),
J. Fischer (Tübingen, Germany),
A. Henschel (Berlin, Germany),
S. Plank-Habibi (Alzenau, Germany),
B. Schilling (Passau, Germany),
A. Kleinheinz (Buxtehude, Germany),
K. Schäkel (Heidelberg, Germany),
N. Papadopoulos (Athen, Greece),
M. Kowalski (Lodz, Poland),
M. Fernandez-Rivas (Madrid, Spain),
K. Solarewicz-Madajek (Wroclaw, Poland),
C. Körner-Rettberg (Bochum, Germany),
T. Mustakov (Sofia, Bulgaria),
K. Hartmann (Lübeck, Germany),
C. Kemen (Hamburg, Germany),
U. Miehe (Leipzig, Germany),
C. Ebner (Vienna, Austria),
S. Haak (Oldenburg, Deutschland),
V. Cardona (Barcelona, Spain),
S. Hämmerling (Heidelberg, Germany),
E. Arroabarren (Pamplona, Spain),
M. Bilo (Ancona, Italy),
N. Cabañes Higuero (Toledo, Spain),
A. Vega Castro (Guadalajara, Spain),
I. Poziomkowska-Gęsicka (Szczecin, Poland),
S. Büsing (Osnabrück, Germany),
U. Klettke (Berlin, Germany),
C. Virchow (Rostock, Germany),
G. Christoff (Sofia, Bulgaria),
U. Jappe (Borstel, Germany),
K. Breuer (Hamburg, Germany),
S. Müller and T. Jakob (Freiburg, Germany),
H. Straube (Darmstadt, Germany),
C. Vogelberg (Dresden, Germany),
F. Knöpfel (Norderney, Germany),
J. Hourihane (Cork, Ireland),
B. Rogala (Silesia, Poland),
A. Montoro (Madrid, Spain),
A. Brandes (Frankfurt/Oder, Germany),
A. Muraro (Padua, Italy),
T. Buck und J. Büsselberg (Hanover-Misburg, Germany),
N. Zimmermann (Potsdam, Germany),
D. Hernandez (Valencia, Spain),
P. Minale (Genua, Italy),
J. Niederwimmer und B. Zahel (Linz, Austria),
A. Fiocchi (Rome, Italy),
A. Reissig (Gera, Germany),
F. Horak (Vienna, Austria),
N. Klossowiski (Düsseldorf, Germany),
F. Eitelberger (Wels, Austria),
H. Ott (Hanover, Germany),
R. Asero (Milan, Italy),
S. Pistauer (Sylt/Westerland, Germany),
M. Geißler (Ribnitz-Damgarten, Germany),
L. Ensina (Sao Paulo, Brazil),
A. Plaza Martin (Barcelona, Spain),
J. Meister (Aue, Germany),
S. Hompes (Hamburg, Germany),
S. Stieglitz (Wuppertal, Germany).

@@

knitr::include_graphics("../figures/diag22.png")
```

>>>>

`r round(elicitorTab[elicitorTab$Elicitor =="food","Food allergy [n]"] / elicitorTab[elicitorTab$Elicitor =="food","n"]*100, 0) `% of food elicited refractory cases had a previously confirmed diagnosis of food allergy. Insect-venom and food allergens most frequently elicited severe cases of anaphylaxis.
Refractory anaphylaxis cases were more often elicited by bees than severe, non-refractory cases, p = `r table(data3$q_340_insects,data3$rANA) %>%  {rbind(addmargins(.[3:8,],1) %>% tail(1),.[2,])} %>% as.matrix() %>% fisher.test() %>% {.$p.value} %>% round(4)` (table \@ref(tab:elicitExact)).

@@

<!-- The influence of tryptase -->
Baseline serum tryptase (BST) levels were increased in patients with refractory anaphylaxis, although only in 7 patients they exceeded the threshold level of 11.5 ng/mL - what is commonly recognized as elevated [@klion2003]. BST may reflect pro-β tryptase due to increased body mast cell content [@CAUGHEY2006] or result from alpha-tryptasemia due to multiple copies of *TPSAB1* gene [@Lyons2018]. Irrespective of the mechanism - increased BST has been shown to correlate with the severity of anaphylaxis [@Aniceto2019].

@@

# Acknowledgements
We thank all patients, parents, and their children for their support in providing data on the
the occurrence of anaphylaxis for this study. We thank the study personnel for patients
counseling and data entry and we thank the members of The European Anaphylaxis Registry
in detail:

```{r, results="asis"}
dfca <-readxl::read_excel("../data/derived_data/Co-authors 2019-08-28.xlsx")
names(dfca) <- "names"
temp <- dfca %>% 
  dplyr::as_tibble() %>% 
  dplyr::filter(!is.na(names)) %>% 
  dplyr::pull(names) %>% 
  paste(collapse = ", ")  %>% 
  cat
```

@@

knitr::include_graphics("../figures/diag.png")
```
